This Community Rules Reference Guide (CRRG) is a comprehensive cross-reference and resource for all Dungeon Alliance rules. Unlike the rulebook and rules supplement from the base game, it addresses complex and unusual game-play situations.

This community reference covers the following areas:
\begin{itemize}
\item Rules from the base game including rules supplement and all released expansions
\item Visual examples for "Movement", "Line of Sight" and "Special
Situations in Combat"
\item Tables with overviews on the content of the base game and expansions
\item An index with hyperlinked page numbers
\end{itemize}

\textbf{Section \ref*{sec:RulesReferenceGuide}} lists the rules of the game in alphabetical order. It should allow players to quickly find answers to questions during gameplay by looking up the entry in question. Each entry includes the basic rules, with exceptions and additional clarifications. Related topics below each entry link to other entries that hold additional information.

\textbf{Section \ref*{sec:ErrataAndFAQ}} contains errata and frequently asked questions. Here you can find clarifications for example on how a certain card effect is meant to be played.

\textbf{Section \ref*{sec:Appendix}} contains different tables detailing for example the content of the game and it's expansions.

\noindent\hfil\rule{2cm}{.2pt}\hfil

\textbf{DISCLAIMER:} This document is currently very incomplete and should not be used as a reference for the game in it's current form.

\noindent\hfil\rule{2cm}{.2pt}\hfil

This CRRG is a fan-made guide and might not offer the same level of quality as the official rule books. Mistakes and typos are very probable. All feedback is wholeheartedly welcome!

This guide has been very much influenced by the excellent \myuline{\href{http://descent-community.org/index.php/crrg/}{Descent Community Rules Reference Guide}} available for Descent: Journeys in the Dark Second Edition and maintained by \textbf{Sadgit}.

\noindent\hfil\rule{2cm}{.2pt}\hfil

Quixotic Games LLC has generously given the permission to include text excerpts, images and artwork from the official rulebooks. This material is Copyright 2017 Quixotic Games LLC.